Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-01-22 Report/appendix_tightness.tex
convergence_proof

In order for the constraints \eqref{eqn-6.2} and \eqref{eqn-6.3} to be active, there should be at least one user per \ac{BS} with large enough backlogged packets that cannot be satisfied with the given power budget. To prove this, let us consider a single \ac{BS} \me{N_T \times 1} system with \me{|U|_b} users each with \me{Q_k} backlogged packets. Let us consider the problem for a single \ac{BS} \me{b} as 
\begin{IEEEeqnarray}{rCl}
	\underset{\gamma_{k},\mvec{m}{k},\beta_{k}}{\text{minimize}} &\quad& \sum_{k \in \mc{U}_b} \big | Q_k - \log_2(1 + \gamma_k) \big |^q  \eqsub \\
	\text{subject to} &\quad& \gamma_{k} \leq \frac{ | \mvec{H}{k} \mvec{m}{k}|^2}{\beta_{k}} \IEEEyessubnumber \label{ae-1} \\
	&\quad& \beta_{k} \geq N_0 + \sum_{\mathclap{i \neq k}} |\mvec{H}{k} \mvec{m}{i} |^2 \IEEEyessubnumber \label{ae-2} \\
	&\quad& \sum_{k \in \mc{U}_b} \text{tr} \, (\mvec{m}{k} \mvec{m}{k}^\herm) \leq P_{{\max}}. \IEEEyessubnumber \label{ae-3}
\end{IEEEeqnarray}
Let \me{N_T > |\mc{U}_b|} and the precoders are designed for all users. Let us consider two users, say \me{i} and \me{j}, whose precoders are given by \me{\mvec{m}{i}} and \me{\mvec{m}{j}}. In order to show that the constraint \eqref{ae-1} and \eqref{ae-2} are tight for all users at optimal when the objective has non zero value at the final solution. Let us assume by contradiction that \eqref{ae-1} and \eqref{ae-2} are not tight for user \me{i} only. Let us also consider that \me{\gamma_k} for all users \me{k \in \mc{U}_b \backslash j} are identified to satisfy the backlogged packets.

Now, in order to minimize the objective of the \me{\ith{i}} user, \me{\gamma_i} should be \me{2^{Q_i} - 1} to have the minimum objective. Since the constraints \eqref{ae-1} and \eqref{ae-2} are not tight for the \me{\ith{i}} user, the actual \ac{SINR} on the r.h.s of \eqref{ae-1} is greater than \me{\gamma_i} of the user \me{i}. It is attributed to the excess power in the transmit precoder of user \me{i} as \me{\mvec{m}{i} = \bar{\mbf{m}}_{i} + \mbf{V}_i \mbf{e}}, where \me{\mbf{V}_i = \mc{N}([\mbf{H}^{\mathrm{T}}_0, \dotsc, \mbf{H}^{\mathrm{T}}_{i-1},\mbf{H}^{\mathrm{T}}_{i+1}, \dotsc,\mbf{H}^{\mathrm{T}}_{|\mc{U}_b| - 1}]^{\mathrm{T}})} denotes the null space corresponding to the other user channel vectors and \me{\mbf{e}} is any random vector with power \me{\Delta P}. Note that this extra power has no impact on the interference constraint \eqref{ae-2} of other users.

Since the power is not utilized efficiently, the objective will force the excess \me{\Delta P} to be used for the starving user \me{j} with the non zero objective value with the current precoder \me{\mvec{m}{j}}. In order to minimize the objective, we can find a vector \me{\mvec{m}{j} = \bar{\mbf{m}}_{j} + \mbf{V}_j \mbf{e}}, which has no impact on the interference or the optimal precoders of other users and their objective value, still minimize the objective function. It is in contradiction to our original assumption that the power is utilized for the user \me{i} making the constraints loose. It can be seen that the constraints are tight as long as there is one user with unserviced backlogged packets at each \ac{BS} with the given power budget. Since the objective is not to minimize the power, when the power budget is more than sufficient to service the backlogged packets of all users, the \ac{JSFRA} scheme is not guaranteed to find the minimum power precoders to minimize the current backlogged packets in the system.

>>>>

In order for the constraints \eqref{eqn-6.2} and \eqref{eqn-6.3} to be active, there should be at least one user per \ac{BS} with large enough backlogged packets that cannot be satisfied with the given power budget. To prove this, let us consider a single \ac{BS} \me{N_T \times 1} system with \me{|U|_b} users each with \me{Q_k} backlogged packets. Let us consider the problem for a single \ac{BS} \me{b} as 
\begin{IEEEeqnarray}{rCl}
	\underset{\gamma_{k},\mvec{m}{k},\beta_{k}}{\text{minimize}} &\quad& \sum_{k \in \mc{U}_b} \big | Q_k - \log_2(1 + \gamma_k) \big |^q  \eqsub \\
	\text{subject to} &\quad& \gamma_{k} \leq \frac{ | \mvec{H}{k} \mvec{m}{k}|^2}{\beta_{k}} \IEEEyessubnumber \label{ae-1} \\
	&\quad& \beta_{k} \geq N_0 + \sum_{\mathclap{i \neq k}} |\mvec{H}{k} \mvec{m}{i} |^2 \IEEEyessubnumber \label{ae-2} \\
	&\quad& \sum_{k \in \mc{U}_b} \text{tr} \, (\mvec{m}{k} \mvec{m}{k}^\herm) \leq P_{{\max}}. \IEEEyessubnumber \label{ae-3}
\end{IEEEeqnarray}
Let us assume the system has \me{N_T > |\mc{U}_b|} and the precoders are determined for all users at the optimal point for which the objective is minimum and is nonzero. Let us consider two users, say \me{i} and \me{j} with precoders \me{\mvec{m}{i}} and \me{\mvec{m}{j}}. In order to show the tightness of the constraints \eqref{ae-1} and \eqref{ae-2}, let us assume by contradiction that \eqref{ae-1} and \eqref{ae-2} are not tight for a user \me{i} only. Let us also consider that \me{\gamma_k} for all users \me{k \in \mc{U}_b \backslash j} are identified to satisfy the backlogged packets.

Now, in order to minimize the objective of the \me{\ith{i}} user, \me{\gamma_i} should be \me{2^{Q_i} - 1} to have the minimum objective. Since the constraints \eqref{ae-1} and \eqref{ae-2} are not tight for the \me{\ith{i}} user, the actual \ac{SINR} on the r.h.s of \eqref{ae-1} is greater than \me{\gamma_i}. It is attributed to the excess power in the transmit precoder of user \me{i} as \me{\mvec{m}{i} = \bar{\mbf{m}}_{i} + \mbf{V}_i \mbf{e}}, where \me{\mvec{V}{i} = \mc{N}([\mbf{H}^{\mathrm{T}}_0, \dotsc, \mbf{H}^{\mathrm{T}}_{i-1},\mbf{H}^{\mathrm{T}}_{i+1}, \dotsc,\mbf{H}^{\mathrm{T}}_{|\mc{U}_b| - 1}]^{\mathrm{T}})} denotes the null space corresponding to the other user channel vectors and \me{\mbf{e}} be any random vector with power \me{\Delta P}. Note that the extra power has no impact on the interference constraint \eqref{ae-2} of other users.

Since the allocated rate of user \me{j} is less than the queued packets, we can find a precoder \me{\mvec{m}{j}} with the additional power of \me{\Delta P} as \me{\mvec{m}{j}^\prime = \bar{\mbf{m}}_{j} + \mvec{V}{j} \mbf{e}^\prime}. Note that the new precoder has no impact on the interference constraint of other users. The newly found precoder \me{\mvec{m}{j}^\prime} minimize the queue of user \me{j} without affecting other user rates, there by reduces the objective further. It is in contradiction to our original assumption that the power is utilized for the user \me{i} making the constraints loose. It can be seen that the constraints are tight as long as there is one user with unserviced backlogged packets at each \ac{BS} with the given power budget. Since the objective is not to minimize the power, when the power budget is more than sufficient to service the backlogged packets of all users, the \ac{JSFRA} scheme is not guaranteed to find the minimum power precoders to minimize the current backlogged packets in the system.

### 2015-01-22 Report/convergence_centralized.tex
convergence_proof

\newcommand{\mx}{\mbf{x}}
\newcommand{\my}{\mbf{y}}
\newcommand{\mz}{\mbf{z}}

\newcommand{\mxb}{{\mbf{x}}}
\newcommand{\myb}{{\mbf{y}}}
\newcommand{\iterate}[2]{{#1}^{(#2)}}

Let us write the \ac{JSFRA} problem in \eqref{eqn-6} and \eqref{eqn-mse-1} as
\begin{IEEEeqnarray}{RCL} \label{con}
\underset{\mx,\my,\mz}{\text{minimize}} &\quad& f(\mz) \eqsub \label{con-obj} \\
\text{subject to} &\quad& h(\mz) - g_0(\mx,\my) \leq 0 \eqsub \label{con-dc} \\
&\quad& g_1(\mx,\my) \leq 0, \eqsub \label{con-cvx-blk} \\
&\quad& g_2(\mx) \leq 0, \eqsub \label{con-cvx}
\end{IEEEeqnarray}
wher \me{g_2,f} are convex functions and \me{h} is a linear function. Let \me{g_0,g_1} are convex functions only on \me{\mx} or \me{\my} as the variable but not on both. Note that the \eqref{con-dc} correspond to the constraints in \eqref{eqn-6.2} and \eqref{eqn-mse-1.2} and \eqref{con-cvx-blk} corresponds to the constraints in \eqref{eqn-6.3} and \eqref{eqn-mse-1.3}. Other convex constraints are addressed by the constraint \eqref{con-cvx}. With this, the feasible set of the problem \eqref{con} is given by 
\begin{IEEEeqnarray}{rl}
\mc{F} &= \{ \mx,\my,\mz | h(\mz) - g_0(\mx,\my) \leq 0, g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0\} \eqspace
\end{IEEEeqnarray}

Before proceeding further, let us define the following notations. Let \me{\iterate{\mx}{k}} denote the \me{\ith{k}} \ac{BCDM} operating point and \me{\mx_k} represent the \me{\ith{k}} \ac{SCA} approximation point. Since the problem \eqref{con} is nonconvex, it is not guaranteed to find an optimal solution. In order to solve for a suboptimal solution, let us resort to the \ac{BCDM} by fixing a block of variables and optimize for others. Since \ac{BCDM} is an iterative method, let us initialize the variable \me{\my} as \me{\iterate{\myb}{0} \in \mc{F}}. Now the problem in \eqref{con} is still nonconvex due to the constraint \eqref{con-dc}, which is now in \ac{DC} form. Following the approach presented in \cite{lipp2014variations,lanckriet2009convergence}, the function \me{g_0(\mx,\iterate{\myb}{0})} is majorized around \me{\mxb_0 \in \mc{F}} as
\begin{equation} \label{con-relax}
\hat{g}_o(\mx,\iterate{\myb}{0};\mxb_0) = {g}_0(\mxb_0,\iterate{\myb}{0}) + \nabla g_0(\mxb_0,\iterate{\myb}{0})^\mathrm{T} (\mx - \mx_0).
\end{equation}
Using the relaxation \eqref{con-relax}, the convex subproblem for the \me{\ith{i}} \ac{BCDM} iterate of \me{\myb} and the \me{\ith{k}} linear approximation of \me{\mxb} as
\begin{IEEEeqnarray}{RCL} \label{con-m}
	\underset{\mx,\my,\mz}{\text{minimize}} &\quad& f(\mz) \eqsub \label{con-obj-m} \\
	\text{subject to} &\quad& h(\mz) - \hat{g}_0(\mx,\iterate{\myb}{i};\mx_k) \leq 0 \eqsub \label{con-dc-m} \\
	&\quad& g_1(\mx,\iterate{\myb}{i}) \leq 0, \eqsub \label{con-cvx-blk-m} \\
	&\quad& g_2(\mx) \leq 0, \eqsub \label{con-cvx-m}
\end{IEEEeqnarray}
Let the set defined by the problem in \eqref{con-relax} be represented as \me{\iterate{\mc{F}}{i}_k}. In order to prove the convergence of the convex subproblems \eqref{con-relax} for a fixed \me{\iterate{\myb}{i}}, let us assume that \eqref{con-relax} yields \me{\mx_{k+1}} as the final solution at the \me{\ith{k}} iteration. To show that \me{\mx_{k+1}} minimizes the objective function, let us assume that the previous point \me{\mx_k} is feasible around which the relaxation is made. It can be seen that 
\begin{equation*}
h(\mz) - {g}_0(\mx,\iterate{\myb}{i}) \leq h(\mz) - \hat{g}_0(\mx,\iterate{\myb}{i};\mxb_k) \leq 0
\end{equation*}

>>>>

\newcommand{\eqn}[1]{\(#1\)}
\newcommand{\mx}{\mbf{x}}
\newcommand{\my}{\mbf{y}}
\newcommand{\mz}{\mbf{z}}
\newcommand{\mxb}{{\mbf{x}}}
\newcommand{\myb}{{\mbf{y}}}
\newcommand{\iterate}[2]{{#1}^{(#2)}}

Let us write the \ac{JSFRA} problem in \eqref{eqn-6} and \eqref{eqn-mse-1} as
\begin{IEEEeqnarray}{rCl} \label{con}
\underset{\mx,\my,\mz}{\text{minimize}} &\quad& f(\mz) \eqsub \label{con-obj} \\
\text{subject to} &\quad& h(\mz) - g_0(\mx,\my) \leq 0 \eqsub \label{con-dc} \\
&\quad& g_1(\mx,\my) \leq 0, \eqsub \label{con-cvx-blk} \\
&\quad& g_2(\mx) \leq 0, \eqsub \label{con-cvx}
\end{IEEEeqnarray}
wher \me{g_2,f} are convex functions and \me{h} is a linear function. Let \me{g_0,g_1} are convex functions only on \me{\mx} or \me{\my} as the variable but not on both. Note that the \eqref{con-dc} correspond to the constraints in \eqref{eqn-6.2} and \eqref{eqn-mse-1.2} and \eqref{con-cvx-blk} corresponds to the constraints in \eqref{eqn-6.3} and \eqref{eqn-mse-1.3}. Other convex constraints are addressed by the constraint \eqref{con-cvx}. With this, the feasible set of the problem \eqref{con} is given by 
\begin{IEEEeqnarray}{rl}
\mc{F} &= \{ \mx,\my,\mz | h(\mz) - g_0(\mx,\my) \leq 0, g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0\} \nonumber
\end{IEEEeqnarray}

Before proceeding further, let us define the following notations. Let \me{\iterate{\mx}{k}} denote the \me{\ith{k}} \ac{BCDM} operating point and \me{\mx_k} represent the \me{\ith{k}} \ac{SCA} approximation point. Since the problem \eqref{con} is nonconvex, it is not guaranteed to find the optimal solution. In order to solve for a suboptimal solution, let us resort to the \ac{BCDM} by fixing a block of variables and optimize for others. Since \ac{BCDM} is an iterative method, let us initialize the variable \me{\my} as \me{\iterate{\myb}{0} \in \mc{F}}. Now the problem in \eqref{con} is still nonconvex due to the constraint \eqref{con-dc}, which is in \ac{DC} form. Following the approaches presented in \cite{lipp2014variations,lanckriet2009convergence}, the function \me{g_0(\mx,\iterate{\myb}{0})} is majorized around a feasible point \me{\mxb_0 \in \mc{F}} as
\begin{equation} \label{con-relax}
\hat{g}_o(\mx,\iterate{\myb}{0};\mxb_0) = {g}_0(\mxb_0,\iterate{\myb}{0}) + \nabla g_0(\mxb_0,\iterate{\myb}{0})^\mathrm{T} (\mx - \mx_0).
\end{equation}
Using the relaxation \eqref{con-relax}, the convex subproblem for the \me{\ith{i}} \ac{BCDM} iterate of \me{\myb} and the \me{\ith{k}} linear approximation of \me{\mxb} as
\begin{subeqnarray} \label{con-m}
	\underset{\mx,\my,\mz}{\text{minimize}} &\quad& f(\mz) \eqsub \label{con-obj-m} \\
	\text{subject to} &\quad& h(\mz) - \hat{g}_0(\mx,\iterate{\myb}{i};\mx_k) \leq 0 \eqsub \label{con-dc-m} \\
	&\quad& g_1(\mx,\iterate{\myb}{i}) \leq 0, \eqsub \label{con-cvx-blk-m} \\
	&\quad& g_2(\mx) \leq 0, \eqsub \label{con-cvx-m}
\end{subeqnarray}
Let the set defined by the problem in \eqref{con-relax} be represented as \me{\iterate{\mc{F}}{i}_k}. In order to prove the convergence of the convex subproblem \eqref{con-m} for a fixed \me{\iterate{\myb}{i}} and \me{\mx_k}, let us assume that \eqref{con-m} yields \me{\mx_{k+1}} and \me{\mz_{k+1}} as the solution at the \me{\ith{k}} iteration. To show that \me{\mx_{k+1}} and \me{\mz_{k+1}} minimizes the objective function ans also feasible, let us assume that the point \me{\mx_k} is feasible for \eqref{con-m}. Since the function \me{{g}_0(\mx,\iterate{\myb}{i})} is linearized around \me{\mx_k}, it satisfies
\begin{equation}
h(\mz) - {g}_0(\mx,\iterate{\myb}{i}) \leq h(\mz) - \hat{g}_0(\mx,\iterate{\myb}{i};\mxb_k) \leq 0,
\end{equation}
since \me{{g}_0(\mx,\iterate{\myb}{i}) \leq \hat{g}_0(\mx,\iterate{\myb}{i};\mxb_k), \forall \mx \in \iterate{\mc{F}}{i}_{k-1}}, where \me{\mc{F}_0 = \mc{F}}. Now, \me{\mx_{k+1}} is the solution and feasible for the \me{\ith{k}} subproblem, therefore, it satisfies
\begin{multline}
h(\mz_{k+1}) - {g}_0(\mx_{k+1},\iterate{\myb}{i}) \leq h(\mz_{k+1}) - \hat{g}_0(\mx_{k+1},\iterate{\myb}{i};\mxb_k) \\
\leq h(\mz_{k}) - \hat{g}_0(\mx_{k},\iterate{\myb}{i};\mxb_k) \leq 0. \label{con-sub-set}
\end{multline}
Using \eqref{con-sub-set}, we can prove that the solution \me{\mx_{k+1}} and \me{\mz_{k+1}} are feasible, since the initial point \me{\mx_{0}} was chosen to be feasible. In order to prove the convergence of the objective, using \eqref{con-sub-set}, we can see that \me{\iterate{\mc{F}}{i}_{0} \subseteq \dotsc \subseteq \iterate{\mc{F}}{i}_{k-1} \subseteq \iterate{\mc{F}_k}{i} \subseteq \mc{F}}. Since at \me{\ith{k}} iteration, the feasible set of the problem \eqref{con-m} includes the feasible sets of the earlier iteration, we can see that 
\begin{equation} \label{con-convergence}
f(\mz_0) \geq f(\mz_k) \geq f(\mz_{k+1}) \geq f(\mz_{\ast,y,i}). 
\end{equation}
Thus the sequence \me{f(\mz_k)} is nonincreasing and converges to a critical point. Let \me{\mx_{\ast}} and \me{\mz_{\ast,y,i}} be the optimal point of the problem \eqref{con-m} when the iterative algorithm is converged. The symbol \me{y,i} in \me{\mz_{\ast,y,i}} denotes the optimal \me{\mz} with fixed \me{\my} at the \eqn{\ith{i}} \ac{BCDM} iteration. It can be seen from \cite{marks1978technical} that the optimal point of the converged subproblems is in deed the stationary point of the original nonconvex problem \eqref{con}. It can be easily verified by the \ac{KKT} expressions and the feasibility of the constraints.

Once the optimal solution is found for the fixed \me{\my}, we fix the variable \me{\mx} as \me{\iterate{\mxb}{i} = \mx_{\ast}} and optimize \me{\my}. The problem is still nonconvex due to the \ac{DC} constraint. By following similar approach as we discussed for the variable \me{\mx}, we can obtain the optimal solution \me{\my_{k}} for the convex subproblem at the \me{\ith{k}} iteration. The convergence and the nonincreasing behavior of the problem follows similar explanations. Now, the optimal solution of the converged subproblem with \me{\my} as variable is \me{\my_{\ast}} and \me{\mz_{\ast,x,i}}. Following the arguments presented in \cite{marks1978technical}, the optimal point of the converged convex subproblems is a stationary point of the nonconvex problem in \eqref{con}.

Finally, to prove the global convergence of the objective, we need to show the nonincreasing behavior of the objective function between each \ac{BCDM} update, \textit{i.e}, \me{f_0(\mz_{\ast,y,i}) \geq f_0(\mz_{\ast,x,i}) \geq f_0(\mz_{\ast,y,i+1})}. Let us assume that for an initial feasible value of \eqn{\my} at \eqn{\iterate{\my}{0}}, we achieve a stationary point of \eqref{con} by solving sequence of convex subproblems. The solution is given by \eqn{\mz_{\ast,y,0}} and \eqn{\mx_{\ast}}. Now, by fixing \eqn{\iterate{\mx}{0} = \mx_{\ast}}, we find the optimal solution \eqn{\mz_{\ast,x,0}} and \eqn{\my_{\ast}} by solving the convex subproblems. It can be seen that 
\begin{equation}
f_0(\mz_{k,y,0}) \geq f_0(\mz_{\ast,y,0}) \geq f_0(\mz_{0,x,0}) \geq f_0(\mz_{\ast,x,0}),
\end{equation}
which follows from the convexity of the objective function \eqn{f_0} and the initial \eqn{\iterate{\my}{0}} is also a feasible point for the variable \eqn{\my} of the \eqn{\ith{k}} subproblem. Using the property of induction, we can show that the global problem converges to a stationary point of the nonconvex problem \eqref{con} in a nonincreasing manner.

Note that the uniqueness of the convex subproblems \eqref{con-m} is required for the convergence of the proof. We can prove the uniqueness of the convex subproblems defined by \eqref{eqn-9} and \eqref{eqn-mse-2} using the following constraints. For the problem \eqref{eqn-9}, the uniqueness of the transmit precoders is guaranteed by the constraint \eqref{eqn-8}, which can be written as
\begin{equation}
\gamma_{l,k,n} - \mvec{\tilde{m}}{l,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n} (\mvec{m}{l,k,n} - \mvec{\tilde{m}}{l,k,n}) \leq 0,
\end{equation}
where \eqn{\mvec{\tilde{H}}{b_k,k,n} = \mvec{w}{l,k,n}^\herm \mvec{\tilde{H}}{b_k,k,n}} and for the convex subproblem \eqref{eqn-mse-2}, uniqueness of the transmit precoder is guaranteed by the constraint 
\begin{multline}
| 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} |^2 \\ + \enoise \leq \epsilon_{l,k,n}.
\end{multline}
Using these arguments, we can claim that the proposed \ac{JSFRA} centralized solution achieves a stationary point of the original nonconvex problem with the nonincreasing objective value at each iteration.

### 2015-01-22 Report/ieee_journal.tex
changes with satya
satya_2
convergence_proof

\documentclass[10pt,final,onecolumn,letterpaper]{./../Styles/IEEEtran}

\usepackage{amsmath,amssymb}
\usepackage{acronym,etoolbox}
\usepackage[ruled]{algorithm2e}
\usepackage[dvipdfmx]{graphicx}
\usepackage[subrefformat=parens,labelformat=parens,labelseparator=period,caption=false]{subfig}
\usepackage{subeqnarray,multirow,cite,array,setspace,fixltx2e,mathtools,lineno,verbatim,todonotes,inputenc}

@@

\section{Response to reviewer comments}
\input{review_comments}

@@

\subsection{Reduced Complexity Resource Allocation} \label{sec-3.4}
\input{sub_channel_wsrm}

@@

@@

>>>>

\documentclass[10pt,final,twocolumn,letterpaper]{./../Styles/IEEEtran}

\usepackage{amsmath,amssymb}
\usepackage{acronym,etoolbox}
\usepackage[ruled]{algorithm2e}
\usepackage[dvipdfmx]{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[subrefformat=parens,labelformat=parens,labelseparator=period,caption=false]{subfig}
\usepackage{subeqnarray,multirow,cite,array,setspace,fixltx2e,lineno,verbatim,todonotes,inputenc,mathtools}

@@

%\section{Response to reviewer comments}
%\input{review_comments}

@@

\subsection{Reduced Complexity Resource Allocation} \label{sec-3.4}
\review{\input{sub_channel_wsrm}}

@@

\subsection{Average Backlogged Packets Over Slots}

\review{\input{time_correlated}}

@@

\section{Tightness of \ac{SINR} relaxation} \label{a-3}
\review{\input{appendix_tightness}}
